Homework Report

### 2017-01-30 work/work.tex
Adding heuristic C and example on how it is not optimal

\section*{Heuristics}
In this report, I will discuss multiple vertex coloring heuristics. I will define them as follows:

@@

Heuristic A is the greedy algorithm. The input is a simple graph \(G = (V, E)\).

@@

@@

@@

\subsection*{Example 2}

>>>>

\section*{Heuristics}
In this report, I will discuss multiple vertex coloring heuristics. The input for all heuristics defined here is a simple graph \(G = (V, E)\). I will define them as follows:

@@

Heuristic A is the greedy algorithm.

@@

\subsection*{Heuristic C}

Heuristic C colors a graph by finding maximal independent sets of \(G\).

\begin{algorithm}
\caption{Coloring via maximal independent set algorithm}
\begin{algorithmic}[1]
\While{$G$ is non-empty}
\State Find a maximal independent set of $G$, i.e. $S_i$
\State Color all vertices in $S_i$ with color $p$, where $p$ is the smallest color available
\State Let $G \leftarrow G[V \setminus S_i ] $
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

\begin{prop}
Heuristic C also does not always produce an optimal solution, i.e. it does not always produce a minimum coloring of a graph.
\end{prop}

\subsection*{Example 2}
To show this, I will create another example that satisfies conditions \((1)\) and \((2)\) from above. I've constructed a graph \(K = (V,E)\) for this example.

\begin{figure}[H]
\centering
\includegraphics[scale=0.38]{images/mis-1.png}
\caption{Uncolored original graph \(K\)}
\end{figure}

By applying heuristic C and finding maximal independent sets, we see that \(K\) is \emph{5-colorable}.

\begin{figure}[H]
\centering
\includegraphics[scale=0.38]{images/mis-2.png}
\caption{Coloring of \(K\) after applying heuristic C}
\end{figure}

This is a non-optimal solution. We can see that the subgraph created by vertices \(\{5, 6, 7, 8\}\) is complete and thus we need at least 4 colors. This graph is \emph{4-colorable} however, meaning \(\chi^{*}(K) = 4\). Thus, we can see that heuristic C does not always give us an optimal solution.

\begin{figure}[H]
\centering
\includegraphics[scale=0.38]{images/mis-3.png}
\caption{Optimal coloring of \(K\)}
\end{figure}

@@

\subsection*{Example 3}
